COVID-19 dataset strength

### 2020-06-22 covid_dataset_strength/covid_dataset_strength.Rmd
Use better estimated value

```{r cache=TRUE}
topology <- pureseqtmr::predict_proteome_topology(fasta_filename)
n_proteins <- nrow(topology)
n_tmhs <- sum(tally_tmhs(topology)$n_tmhs)
n_non_tmh_aas <- sum(stringr::str_count(topology$topology, "0"))
n_tmh_aas <- sum(stringr::str_count(topology$topology, "1"))
n_aas <- n_non_tmh_aas + n_tmh_aas
f_aas <- n_tmh_aas / (n_tmh_aas + n_non_tmh_aas)
proteome_size <- n_aas
```

@@

```{r}
p_state_transition <- 0.01
```

Based upon nothing but our gut instinct, we estimate this
chance at `r p_state_transition`.

>>>>

```{r cache=TRUE}
topology <- pureseqtmr::predict_topology(fasta_filename)
n_proteins <- nrow(topology)
n_tmhs <- sum(tally_tmhs(topology)$n_tmhs)
n_non_tmh_aas <- sum(stringr::str_count(topology$topology, "0"))
n_tmh_aas <- sum(stringr::str_count(topology$topology, "1"))
n_aas <- n_non_tmh_aas + n_tmh_aas
f_aas <- n_tmh_aas / (n_tmh_aas + n_non_tmh_aas)
proteome_size <- n_aas
```

@@

This chance we call it `r p_state_transition`.

Based upon simulations (see https://github.com/richelbilderbeek/bbbq_p_trans), we 
estimate `r p_state_transition`:

![](p_trans_0_02.png)

```{r}
p_state_transition <- 0.0494
```
